---
title: "Exam 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# College Scorecard 
mean(college_scorecard$earnings_med)
library(dplyr)
library(tidyr)

mean(college_scorecard$earnings_med, na.rm = T)
sd(college_scorecard$earnings_med, na.rm = T)
var(college_scorecard$earnings_med, na.rm = T)

small_scorecard = college_scorecard[college_scorecard$year=="2014",]
data = college_scorecard[college_scorecard$year== "2015",]
small_scorecard = rbind(small_scorecard, data)
small_scorecard = small_scorecard[small_scorecard$pred_degree_awarded_ipeds=="3",]
small_scorecard1 = small_scorecard[small_scorecard$state_abbr=="TX",]
small_scorecard2 = small_scorecard[small_scorecard$state_abbr=="LA",]
small_scorecard = rbind(small_scorecard1,small_scorecard2)
                    
avgTX = small_scorecard[small_scorecard$state_abbr=="TX",]
avgTX = mean(avgTX$count_working,na.rm=T)
sumTX = small_scorecard[small_scorecard$state_abbr=="TX",]
sumTX = sum(sumTX$count_working,na.rm=T)

avgLA = small_scorecard[small_scorecard$state_abbr=="LA",]
avgLA = mean(avgLA$count_working,na.rm=T)
sumLA = small_scorecard[small_scorecard$state_abbr=="LA",]
sumLA = sum(sumLA$count_working,na.rm=T)

even_smaller_scorecard = data.frame(avgTX,sumTX,avgLA,sumLA)

library(ggplot2)
percent = small_scorecard$count_working / 
(small_scorecard$count_working+small_scorecard$count_not_working
bar = ggplot(even_smaller_scorecard,aes(X=state_abbr, Y=))

```{r}
# Questions on Avocado sales
library(stringr)
avocados  = avocados %>%
  mutate(year = str_sub(date,1,4))
```

```{r}

# Titanic Qs
titanic = Titanic
sum(titanic$female==1) # Counts number of females
sum(titanic$female==0)# Counts number of males
sum(titanic$survived==1)/nrow(titanic) # Percentage of survivors

men = titanic[titanic$female==0,]
women = titanic[titanic$female==1,]

men.survived = sum(men$survived==1)/nrow(men)
women.survived = sum(women$survived==1)/nrow(women)
men.var = var(men$survived)
women.var = var(women$survived)
survivordata = data.frame(men.var,men.survived,women.var,women.survived)
survivordata

library(dplyr)

titanic = titanic %>% mutate(first_class = ifelse(class==1,1,0))
first.class = sum(titanic$first_class==1)
not.first.class = sum(titanic$first_class!=1)
results = data.frame(first.class,not.first.class)
results

```
# Bonus: My Heart Goes on

